Radio Emission from Red-Giant Hot Jupiters

### 2015-12-04 ms.tex
minor edits

Let us also consider the expected number of radio detection from RGHJs taking account of the occurrence rate of Jovian planets. 
For this purpose, we consider an empirical power-law planet occurrence rate described as
%%%
\begin{eqnarray}
f(M_p,P) &\equiv & \frac{d^2N}{d\log M_pd\log P } \\
&=& \mathcal{C} \left( \frac{M_p}{M_{\rm J}} \right)^{\alpha } \left( \frac{P}{1~{\rm days}} \right)^{\beta }
\end{eqnarray}
%%%
where they find $\alpha = -0.31\pm 0.2$, $\beta =0.26 \pm 0.1$, $\mathcal{C} =1.04\times 10^{-3}$  as best-fit values. %
Using this equation, the possibility of a given evolved star in Figure \ref{fig:observability} to have a RGHJ with mass larger than threshold $M_{p0}$ whose radio emission may be detectable is
%%%
\begin{equation}
\mathcal{P }(>M_{p0}) \sim \int_{M_{p0}} d\log M_p\,\int_{P_{\rm min}(M_p)}^{P_{\rm max}(M_p)} d\log P ~f(M_p, P) \label{eq:detect_prob}
\end{equation}
%%%
where $P_{\rm min}(M_p)$ is the minimum orbital period to have cyclotron frequency larger than the ambient plasma frequency, while $P_{\rm max}(M_p)$ is the maximum orbital period given planetary mass to emit detectable radio flux. For the former, combining equations (\ref{eq:fcyc}) and (\ref{eq:fplasma_RG}) leads to
%%%
\begin{eqnarray}
a_{\rm min} (M_p) &=& 2.15~{\rm AU} \left( \frac{M_p}{M_{\rm J}} \right)^{-1.04} \left( \frac{t}{4.5~{\rm Gyr}} \right)^{0.43}  \\
&&\times \left( \frac{\dot M}{10^{-8} M_{\odot}/{\rm yr}} \right)^{1/2} 
\end{eqnarray}
%%%
while for the latter, equations (\ref{eq:scalingB}) and (\ref
{eq:F_nu_RGHJ}) indicate
%%%
\begin{eqnarray}
a_{\rm max} (M_p) &=& 3.80~{\rm AU} \left( \frac{F_{\rm min}}{10~\mu {\rm Jy}} \right)^
{-3/4} \left( \frac{d}{100~{\rm pc}} \right)^{-3/2} \\
&& \times \left( \frac{M_p}{M_{\rm J}} \right)^{-1.04/4}  \left( \frac{t}{4.5~{\rm Gyr}} \right)^{-0.43/4} \\
&& \times \left( \frac{M_{\star }}{10^{-8}~M_{\odot }/{\rm yr}} \right)^{1/2} \left( \frac{v_{\star }}{10^{-1} v_{\odot }} \right)^{5/4} 
\end{eqnarray}
%%%
They are translated into the orbital period via Kepler's law, $P_{\{{\rm min,max}\}} = 2\pi \sqrt{a^3_{\{{\rm min,max}\}} / GM_{\star } }$.

>>>>

Let us also consider the expected number of radio detection from RGHJs taking account of the occurrence rate of Jovian planets. 
For this purpose, we consider an empirical power-law planet occurrence rate described as
%%%
\begin{eqnarray}
f(M_p,P) &\equiv & \frac{d^2N}{d\log M_pd\log P } \\
&=& \mathcal{C} \left( \frac{M_p}{M_{\rm J}} \right)^{\alpha } \left( \frac{P}{1~{\rm days}} \right)^{\beta }
\end{eqnarray}
%%%
where \citet{cumming2008} found $\alpha = -0.31\pm 0.2$, $\beta =0.26 \pm 0.1$, $\mathcal{C} =1.04\times 10^{-3}$  as best-fit values. %
Using this equation, the probability of a given evolved star in Figure \ref{fig:observability} to have a RGHJ with mass larger than threshold $M_{p0}$ whose radio emission may be detectable is
%%%
\begin{equation}
\mathcal{P }(>M_{p0}) \sim \int_{M_{p0}} d\log M_p\,\int_{P_{\rm min}(M_p)}^{P_{\rm max}(M_p)} d\log P ~f(M_p, P) \label{eq:detect_prob}
\end{equation}
%%%
where $P_{\rm min}(M_p)$ is the minimum orbital period to have cyclotron frequency larger than the ambient plasma frequency, while $P_{\rm max}(M_p)$ is the maximum orbital period given planetary mass to emit detectable radio flux. For the former, combining equations (\ref{eq:fcyc}) and (\ref{eq:fplasma_RG}) leads to
%%%
\begin{eqnarray}
a_{\rm min} (M_p) &=& 2.15~{\rm AU} \left( \frac{M_p}{M_{\rm J}} \right)^{-1.04} \left( \frac{t}{4.5~{\rm Gyr}} \right)^{0.43}  \\
&&\times \left( \frac{\dot M_{\star }}{10^{-8}M_{\odot}/{\rm yr}} \right)^{1/2} 
\end{eqnarray}
%%%
while for the latter, equations (\ref{eq:scalingB}) and (\ref
{eq:F_nu_RGHJ}) indicate
%%%
\begin{eqnarray}
a_{\rm max} (M_p) &=& 3.80~{\rm AU} \left( \frac{F_{\rm min}}{10~\mu {\rm Jy}} \right)^
{-3/4} \left( \frac{d}{100~{\rm pc}} \right)^{-3/2} \\
&& \times \left( \frac{M_p}{M_{\rm J}} \right)^{-1.04/4}  \left( \frac{t}{4.5~{\rm Gyr}} \right)^{-0.43/4} \\
&& \times \left( \frac{\dot M_{\star }}{10^{-8}M_{\odot }/{\rm yr}} \right)^{1/2} \left( \frac{v_{\star }}{10^{-1} v_{\odot }} \right)^{5/4} 
\end{eqnarray}
%%%
They are translated into the orbital period via Kepler's law, $P_{\{{\rm min,max}\}} = 2\pi \sqrt{a^3_{\{{\rm min,max}\}} / GM_{\star } }$.
